Nail: A practical interface generator for binary formats

### 2014-04-01 paper/intro.tex
line-wrap intro and relwk

% For a long time, it has been possible to write a concise and precise specification of what a data
% format looks like, feed it to a tool and let it generate a parser and potentially a generator for
% that format. However, instead of using these tools, programmers have continued to laboriously
% hand-write bug-prone input/output code. One of the reasons they have done so is that existing tools
% were geared towards parsing text-based programming languages, not for dealing with binary protocols,
% although the underlying algorithms remain the same.

\subsection{Problems handling untrusted input}
Code handling untrusted user inputs is most prone to contain security vulnerabilities. While memory
corruption errors or fatal logic flaws can occur anywhere in a program, bugs in the input handling
code are most likely to be exploitable, because an attacker has total control over the inputs to
that code.

@@

\subsection{Parser generators}
%%TODO
Luckily, we can avoid all of these problems at once if we have a single, executable specification of
what exactly a programs input is supposed to look like. In fact, definitive grammars have long
been written for all sorts of protocols and are the standard way of describing text-based protocols.
Parser generators can automatically create parsers for such languages, and with common classes of
grammars such as regular expressions or deterministic context free languages, that parser can be
expressed in a computationally less powerful form, e.g. a finite automaton or a push down automaton,
limiting the weird machine problem and enabling very efficient implementation~\cite{Knuth1965607}.

@@

\subsection{Motivation}
\paragraph{Motivation}
While it is possible to express short transformations on the input entirely as semantic actions\footnote{This is in fact the design rationale, to perform computation on the fly as the parser
  walks the parse tree.}, more complicated programs usually construct an internal representation,
which contains all relevant information from the input in a format native to the programming
language used. For example, a C programmer ideally wants to deal with structs and NULL-terminated
arrays, whereas a C++ programmer might expect STL containers, a Java programmer interfaces, a
Haskell programmer records and a LISP programmer property lists. 
 The structure of this internal representation usually resembles the structure of the grammar.

>>>>

\subsection{Problems handling untrusted input}

Code handling untrusted user inputs is most prone to contain security
vulnerabilities. While memory corruption errors or fatal logic flaws
can occur anywhere in a program, bugs in the input handling code are
most likely to be exploitable, because an attacker has total control
over the inputs to that code.

@@

\subsection{Parser generators}

Luckily, we can avoid all of these problems at once if we have a single,
executable specification of what exactly a programs input is supposed
to look like. In fact, definitive grammars have long been written for
all sorts of protocols and are the standard way of describing text-based
protocols.  Parser generators can automatically create parsers for such
languages, and with common classes of grammars such as regular expressions
or deterministic context free languages, that parser can be expressed
in a computationally less powerful form, e.g. a finite automaton or a
push down automaton, limiting the weird machine problem and enabling
very efficient implementation~\cite{Knuth1965607}.

@@

\subsection{Motivation}

\paragraph{Motivation}

While it is possible to express short transformations on the input
entirely as semantic actions\footnote{This is in fact the design
rationale, to perform computation on the fly as the parser walks the
parse tree.}, more complicated programs usually construct an internal
representation, which contains all relevant information from the input
in a format native to the programming language used. For example, a C
programmer ideally wants to deal with structs and NULL-terminated arrays,
whereas a C++ programmer might expect STL containers, a Java programmer
interfaces, a Haskell programmer records and a LISP programmer property
lists.  The structure of this internal representation usually resembles
the structure of the grammar.
